\documentclass[9pt,a4paper,oneside, onecolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage[english, german]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{gchords}
\usepackage{multicol}
\usepackage{mdframed} 
\author{Tenacious D}
\title{Kickapoo}
\pagestyle{empty}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

\newcommand{\Am}{\upchord{Am}}
\newcommand{\A}{\upchord{A}}
\newcommand{\Dm}{\upchord{Dm}}
\newcommand{\F}{\upchord{F}}
\newcommand{\Fism}{\upchord{F$\sharp$m}}
\newcommand{\Hm}{\upchord{Hm}}
\newcommand{\Hb}{\upchord{H$\flat$}}
\newcommand{\Hbs}{\upchord{H$\flat$7}}
\newcommand{\C}{\upchord{C}}
\newcommand{\Cg}{\upchord{C/G}}
\newcommand{\Em}{\upchord{Em}}
\newcommand{\Gs}{\upchord{G7}}
\newcommand{\G}{\upchord{G}}
\newcommand{\Gis}{\upchord{G$\sharp$}}
\newcommand{\D}{\upchord{D}}
\newcommand{\Dis}{\upchord{D$\sharp$}}
\newcommand{\x}[1]{\upchord{#1}}
\newcommand{\Af}{\upchord{A5}}
\newcommand{\Cf}{\upchord{C5}}
\newcommand{\Gf}{\upchord{G5}}
\newcommand{\Gisf}{\upchord{G$\sharp$5}}
\newcommand{\Ff}{\upchord{F5}}
\newcommand{\Hbf}{\upchord{H$\flat$5}}
\newcommand{\Df}{\upchord{D5}}


\begin{verse}
\textbf{[Jack Black (Narrator)]}\\
\mbox{
\chord{t}{x,x,n,p2,p3,p1}{Dm}
\chord{t}{x,n,p2,p2,p1,n}{Am}
\chord{t}{f1p1,p3,p3,p2,pf1p1,f1p1}{F}
\chord{t}{p3,p2,n,n,n,p3}{G}
\chord{t}{p3,p3,p2,n,p1,n}{C/G}
}\\
A \Dm{}long ass fuckin' time ago, In a town called Kickapoo,\\
There \Am{}lived a humble family: Religious through and through.\\
But \F{}yay there was a black sheep and he \Cg{}knew just what to \G{}do. \\
His name was young J.B. and he refused to step in-line.\\
A vision he did see-eth Fuckin' rockin' all the time.\\
He wrote a tasty jam and all the planets did align\\
\end{verse}

\begin{verse}
\textbf{[Jack Black (Son)]}\\
\mbox{
\chord{5}{p1,p3,p3,x,x,x}{A5}
\chord{8}{p1,p3,p3,x,x,x}{C5}
\chord{3}{p1,p3,p3,x,x,x}{G5}
\chord{6}{p1,p3,p3,x,x,x}{H$\flat$5}
\chord{5}{x,p1,p3,p3,x,x}{D5}
}\\
Oh the \Af{}dragons balls were blazin' as I \Cf{}stepped into his cave,\\
Then I \Gf{}sliced his fuckin' cockles, with a \Hbf{}long and shiny blade!\\
'Twas I who fucked the dragon, fuckalize sing-fuckaloo!\\
And if you try to fuck with me, then I shall fuck you \Af{}too!\\
Gotta get it \Cf{}on in the party \Gf{}zone! \Af{}\qquad\Df{}\qquad\Af{}\\
I got to shoot a load in the party zone!\\
Gotta lick a toad in the party zone!\\
Gotta suck a chode in the party zone! [Crying]\\
\end{verse}

\begin{verse}
\textbf{[Meat Loaf (Father)]}\\
\mbox{
\chord{3}{f1p1,p3,p3,p2,f1p1,f1p1}{G}
\chord{6}{f1p1,p3,p3,p2,f1p1,f1p1}{H$\flat$}
\chord{1}{f1p1,p3,p3,p2,f1p1,f1p1}{F}
\chord{4}{f1p1,p3,p3,p2,f1p1,f1p1}{G$\sharp$}
\chord{x}{f1p1,p3,f1p1,f4p3,f1p1,f1p1}{sus4-Var.}
\chord{3}{x,f1p1,p3,p3,x,x}{C5}
}\\
You've \G{}disobeyed my orders, son, why \Hb{}were you ever born?.\\
Your \F{}brother's ten times better than you, \Gis{}Jesus loves him more.\\
This music that you play for us comes from the depths of hell.\\
Rock and roll's the Devil's work, he wants you to rebel.\\
You'll become a mindless puppet; Beelzebub will pull the strings!\\
Your heart will lose direction, and chaos it will \G{}bring.\\
You'd better shut your \Hb{}mouth, better watch your \F{}tone!\G{}\qquad\Cf{}\qquad\G{}\\
You're grounded for a week with no telephone!\\
Don't let me here you cry, Don't let me hear you moan!\\
You gotta praise The Lord when you are in my home!\\
\end{verse}

\begin{verse}
\textbf{[Jack Black (Son)]}\\
\mbox{
\chord{3}{x,x,p3,p2,f1p1,f1p1}{G}
\chord{6}{x,x,p3,p2,f1p1,f1p1}{H$\flat$}
\chord{1}{x,x,p3,p2,f1p1,f1p1}{F}
\chord{4}{x,x,p3,p2,f1p1,f1p1}{G$\sharp$}
\chord{x}{x,x,p3,p2,f1p1,f4p3}{Var. A}
\chord{x}{x,x,p3,f4p3,f1p1,f1p1}{Var. B}
\chord{3}{x,f1p1,p3,p3,x,x}{C5}
}\\
\G{}Dio can you hear me? I am \Hb{}lost and so alone.\\
I'm \F{}askin' for your guidance. Won't you \Gis{}come down from your throne?\\
I need a tight compadre who will teach me how to rock.\\
My father thinks you're evil, but man, he can suck a cock.\\
Rock is not The Devil's work, it's magical and rad.\\
I'll never rock as long as I am stuck here with my dad...
\Gf{}\qquad\Gisf{}\qquad\Ff{}\qquad\Hbf{}\qquad\Gisf{}

\end{verse}
\begin{verse}
\textbf{[Ronnie James Dio (Dio poster)]}\\
\mbox{
\chord{3}{f1p1,p3,p3,p2,f1p1,f1p1}{G}
\chord{3}{x,f1p1,p3,p3,x,x}{C5}
\chord{1}{p1,p3,p3,x,x,x}{F5}
\chord{4}{p1,p3,p3,x,x,x}{G$\sharp$5}
\chord{3}{p1,p3,p3,x,x,x}{G5}
\chord{6}{x,f1p1,p3,p3,p2,f1p1}{D$\sharp$}
\chord{5}{x,f1p1,p3,p3,p2,f1p1}{D}
\chord{3}{x,f1p1,p3,p3,p2,f1p1}{C}
\chord{8}{x,f1p1,p3,p3,p2,f1p1}{F}
}\\
I \Cf{}hear you brave young Jaybles, you are \Cf{}hungry for the rock.\\
But to \Cf{}learn the ancient method, sacred \Ff{}doors you must unlock.\\
Escape your father's clutches, and this oppressive neighborhood.\\
On a journey you must go, to find the land of Hollywood!\\
In The \Cf{}City of Fallen Angels, where the \Ff{}ocean meets the \Gisf{}sand,\\
You will \Cf{}form a strong alliance, and the \Ff{}world's most \Gf{}awesome \Gisf{}band.\\
To find your fame and fortune, through the valley you must walk.\\
You will face your inner demons. Now go my son and \G{}rock!\Dis{}\qquad\D{}\qquad\qquad\C{}\qquad\D{}\qquad\Dis{}\qquad\F{}


\end{verse}
\begin{verse}
\textbf{[Jack Black (Narrator)]}\\
\mbox{
\chord{3}{f1p1,p3,p3,p2,f1p1,f1p1}{G}
\chord{5}{x,f1p1,p3,p3,p2,f1p1}{D}
\chord{6}{f1p1,p3,p3,p2,f1p1,f1p1}{H$\flat$}
\chord{1}{f1p1,p3,p3,p2,f1p1,f1p1}{F}
\chord{6}{x,f1p1,p3,p3,p2,f1p1}{D$\sharp$}
\chord{3}{x,f1p1,p3,p3,p2,f1p1}{C}

}\\
So he \G{}bailed from fuckin' Kickapoo With hunger in his heart;\\
And he \D{}journeyed far and wide to find the secrets of his art;\\
But \Hb{}in the end he knew that he would \F{}find his counterpart.\\

\G{}Rock.\Dis{}\qquad\D{}\qquad \C{}Ro-\D{}ho-\Dis{}ho-\F{}hock\qquad\G{}\qquad\Dis{}\qquad\D{}\qquad{}...\\
\end{verse}



\end{document}
